The \dealii{} Library, Version 9.0

### 2018-04-06 9.0/paper.tex
Expand major changes section and add references

\item
  Support for Sundials and ROL

@@

% J-P.~Pelteret was supported by the European Research Council (ERC) through the Advanced Grant 289049 MOCOPOLY.
%
% B.~Turcksin: This material is based upon work supported by the U.S. Department of
% Energy, Office of Science, under contract number DE-AC05-00OR22725.
%
%
% D.~Wells was supported by the National Science Foundation (NSF) through Grant
% DMS-1344962.

>>>>

\item
  A dedicated sundials module has been created to provide support for the
  SUNDIALS library. SUNDIALS is a SUite of Nonlinear and
  DIfferential/ALgebraic equations Solvers. ARKode, IDA, and KINSOL are
  supported. ARKode is a solver library that provides adaptive-step time
  integration. IDA is a package for the solution of differential-algebraic
  equations systems in the form $F(t,y,y')=0$. KINSOL is olver for nonlinear
  algebraic systems.

\item 
  A dedicated optimization/rol module has been created to provide support for
  the Rapid Optimization Library (ROL). ROL is a package for large-scale
  optimization.

@@

% J-P.~Pelteret was supported by the European Research Council (ERC) through the Advanced Grant 289049 MOCOPOLY.
%
B.~Turcksin: This material is based upon work supported by the U.S. Department of
Energy, Office of Science, under contract number DE-AC05-00OR22725.
%
%
% D.~Wells was supported by the National Science Foundation (NSF) through Grant
% DMS-1344962.
